### 2022-12-22 response.tex

``Our conclusions echo earlier findings by \cite{gandon2001imperfect}, who showed that vaccine-derived immunity against diseases can promote the evolution of more virulent strains in unvaccinated individuals.
By allowing explicit parasite evolution, they also showed that total malaria mortality peaks at intermediate levels of vaccination; our analysis reveals that the differences in symptomatic and asymptomatic transmission behavior can give rise to the same effect even in the absence of evolution.''

\revtext{Line 58 - "subclinical or even asymptomatic' is imprecise and confusing}

Thank you for pointing this out. We have removed ``or even asymptomatic''

\revtext{Paragraph at line 59 - is the diamond princess data still the best data we have? It would be useful to emphasize that the asymptomatic transmission is very well established.}

Since we are focusing on the asyptomatic transmission of primary infection, we feel that the diamond princess data is one of the best data we have. We have tried to clarify this point while addressing other existing data on asymptomatic transmission:

``It is now well established that asymptomatic individuals can transmit SARS-CoV-2 infections \citep{gao2021role,johansson2021sars,subramanian2021quantifying,koelle2022changing,lizewski2022navy}, but the majority of asymptomatic cases are now driven by prior immunity.
In contrast, the Diamond Princess data provide a unique perspective on the relative transmissibility of immunologically naive asymptomatic individuals.''

\revtext{Paragraph line 69 - It would be useful to discuss how important the symptoms may be for transmission here - coughing, sneezing etc may of course have a direct impact on transmission and it can be this rather than differences in viral loads are likely to be important.}

Thank you for pointing this out. We added the following:

``Notwithstanding similarities in the viral load dynamics, the presence (or the absence) of symptoms further contributes to the uncertainty in the differences in transmissibility of symptomatic and asymptomatic individuals.
In general, coughing and sneezing can help deliver virus containing droplets, the prevalence of presymptomatic and asymptomatic transmission of SARS-CoV-2 suggests speech droplets can also be an important mode of transmission.''

\bibliography{main}

\end{document}
